### 2017-10-17 TreeLevel.tex
updated TreeLevelPlots

\sigma^B(q_i \overline{q}_j \to \tilde{q}\tilde{q}^\dagger) &= \delta_{ij}  \frac{g_s^4}{16\pi s} (n_f-1) \left[ \frac{4}{27} - \frac{16 m_{\tilde{q}}^2}{27s} \right]\nonumber\\

@@

\subsubsection*{The Process $q_i \overline{q}_j \to \tilde{q}\tilde{q}^\dagger$}
The production of a squark and an antisquark through a quark and an antiquark in the initial state originates from two types of Feynman diagrams, see fig. \ref{fig:squarkantisquark}. The first one has an $s$-channel gluon and is the same in the MSSM and in the MRSSM. The second one exhibits a difference due to the $t$-channel gluino which is no Majorana particle in the MRSSM. 
\begin{figure}[!htbp]
\begin{center}
\begin{tikzpicture}[line width=1.0 pt, scale=1.3]
	\draw[fermion] (-1,0.5)--(-0.42,0);
	\draw[fermionbar] (-1,-0.5)--(-0.42,0);
	\draw[gluon] (-0.42,0)--(0.42,0); 
	\draw[scalar] (0.42,0)--(1,0.5);
	\draw[scalarbar] (0.42,0)--(1,-0.5);
\begin{scope}[shift={(3,0)}]
	\draw[fermion] (-1,0.5)--(0,0.5);
	\draw[fermionbar] (-1,-0.5)--(0,-0.5);
	\draw[fermionnoarrow] (0,0.5)--(0,-0.5);
	\draw[gluon] (0,0.5)--(0,-0.5); 
	\draw[scalar] (0,0.5)--(1,0.5);
	\draw[scalarbar] (0,-0.5)--(1,-0.5);
\end{scope}
\end{tikzpicture}
\caption{Tree level diagrams for $q\overline{q} \to \tilde{q}\tilde{q}^\dagger$}\label{fig:squarkantisquark}
\end{center}
\end{figure}
To see this one can either just apply the Feynman rules in Appendix \ref{sec:FeynmanRules} or think of the conservation of $R$-charge: Left handed squarks have R-charge $+1$ and right handed squarks have $R$-charge $-$1. Antiparticles have the opposite $R$-charge of their corresponding particles. The final state particles have to meet the total $R$-charge zero from the initial state. Because of this, one only has $\tilde{q}_L \overline{\tilde{q}}_L$ and $\tilde{q}_R \overline{\tilde{q}}_R$ as the final states in the MRSSM whereas in the MSSM one actually has four instead of two t-channel diagrams: The corresponding final states are $\tilde{q}_L \overline{\tilde{q}}_L$, $\tilde{q}_R \overline{\tilde{q}}_R$, $\tilde{q}_L \overline{\tilde{q}}_R$ and $\overline{\tilde{q}}_R \tilde{q}_L$. Consequently contributions from the $t$-channel diagrams are suppressed in the MRSSM in comparison to the MSSM. As shown in fig. \ref{fig:TreeXsection} this suppression grows with the masses. The reason for this lies in the gluino mass dependence of the $t$-channel diagrams which is explained in the discussion of squark production.\\
If the initial state quarks are of different flavor, the $s$-channel diagram is absent.

@@

\subsection{Results for Squark and Gluino Production at Tree-Level}\label{sec:tree-level_cross_sections}
%REFER TO Kribs, Martin: SNOWMASS WHITEPAPER\\
%REFER TO Vernoica Sanz: How many SUpersymmetries?\\
%\\
This section presents hadronic tree-level (Born) cross sections of squark and gluino production for two colliding protons in both, the MSSM and the MRSSM.\\
Note that in the following all possible production channels are taken into account. This is, for squark and squark-gluino production, also the charged conjugated processes, i.e. $\tilde{q}^\dagger\tilde{q}^\dagger$ and $\tilde{q}^\dagger\tilde{g}\left( \overline{\tilde{g}} \right)$, are included. In addition, squark production counts those processes twice which involve flavor unlike quarks, e.g. $ud \to \tilde{u}\tilde{d}$ is counted twice as the $d$-quark may come from either proton. This applies also to squark-antisquark production through a quark-antiquark pair.\\
The calculations have been performed by a $\texttt{C++}$ code which uses a library containing the absolute squared amplitudes for the processes in question. Note that the author has opted for the absolute squared amplitudes and not the partonic cross sections because this allows also for the calculation of partial differential cross sections, for possible future use. To perform the integration over the Mandelstam variable $t$ and $x_1$ and $x_2$, the routine ``Cuhre'' which is part of the \texttt{CUBA} library\cite{Hahn:2004fe} is used.\\
The following paragraph discusses fig. \ref{fig:TreeXsection}, \ref{fig:TreeLevelSigma_0,9_2} and \ref{fig:TreeXsection5}, i.e. the hadronic cross section of all considered processes for three successive mass ratios of gluino and squark: $\frac{m_{\tilde{g}}}{m_{\tilde{q}}} = 0.9,\ 2$ and $5$. Also, the corresponding fraction of final states is shown.
\begin{figure}[!htpb]
\begin{center}
\includegraphics[scale=.4]{figures/mr=0,9_MSSM+MRSSM}
\includegraphics[scale=.4]{figures/mr=2_MSSM+MRSSM}
\caption{Hadronic cross section for squark and gluino production in the MSSM (left-hand side) and MRSSM (right-hand side) at the LHC with $\sqrt{S} = \unit[13]{GeV}$. The ratio of gluino and squark mass is fixed to 0.9 (first row) and 2 (second row). In the final state it has been summed over all squark flavors exept for $t$-squarks. For the channels $qq \to \tilde{q}\tilde{q}$ and $qG \to \tilde{q}\tilde{G}$ also the charge conjugated process is included. The parton densities used are $\mathtt{MMHT2014LO}$ (LHAPDFID:$25000$) with $\alpha_s(M_Z) = 0.135$ in the 5-flavor scheme \cite{Harland-Lang:2014zoa}. As renormalization and factorization scale $\mu_R = \mu_F = \frac{m_1 + m_2}{2}$ has been chosen, where $m_i$ are the final state particle masses.} \label{fig:TreeXsection}
\end{center}
\end{figure}
\begin{figure}[!htpb]
\begin{center}
\includegraphics[scale=.45]{figures/rel_weights_mr=0,9_MSSM+MRSSM}
\includegraphics[scale=.45]{figures/rel_weights_mr=2_MSSM+MRSSM}
\caption{Relative contributions of the indicated final states on the total hadronic cross section in the MSSM (left-hand side) and MRSSM (right-hand side) at the LHC with \mbox{$\sqrt{S} = \unit[13]{GeV}$}. The ratio of gluino and squark mass is fixed to 0.9 (first row) and 2 (second row). In the final state it has been summed over all squark flavors exept for $t$-quarks. For the channels $qq \to \tilde{q}\tilde{q}$ and $qG \to \tilde{q}\tilde{G}$ also the charge conjugated process is included. The parton densities and the renormalization and factorization scale are chosen as in fig. \ref{fig:TreeXsection}.}\label{fig:TreeLevelSigma_0,9_2}
\end{center}
\end{figure}

For the small mass ratio $\frac{m_{\tilde{g}}}{m_{\tilde{q}}} = 0.9$ and small squark masses, the dominant contribution comes from gluino (antigluino) production. This is even more dominant in the MRSSM which can be explained by the above mentioned factor of two difference in the $GG \to \tilde{g}\tilde{g}(\overline{\tilde{g}})$ channel which comes from the distinguishable gluino and antigluino in the MRSSM. Furthermore there is the above mentioned destructive interference term in the $q\overline{q} \to \tilde{g}\tilde{g}(\overline{\tilde{g}})$ channel which makes the cross section for this process in the MRSSM dominant over the one in the MSSM.\\
For a increasing squark mass, the previously subdominant gluino-squark production takes over and becomes dominant. A salient difference between the MSSM and the MRSSM is that squark production is strongly suppressed in the MRSSM. While in the MSSM it becomes dominant above  $\approx \unit[1400]{GeV}$ it is subsubdominant for the whole displayed squark mass in the MRSSM. This suppression has also already been explained above.\\
Turning from $\frac{m_{\tilde{g}}}{m_{\tilde{q}}} = 0.9$ to $\frac{m_{\tilde{g}}}{m_{\tilde{q}}} = 2$ suppresses quite strongly the production of gluinos in all pertaining channels. For the MSSM one finds above $\unit[500]{GeV}$ a growing dominance of squark production. The same happens in the MRSSM but for a significantly higher squark mass of about $\unit[1200]{GeV}$. This suppression of squark production in the MRSSM increases with a growing gluino masses which can be seen when going from $\frac{m_{\tilde{g}}}{m_{\tilde{q}}} = 0.9$ to  $\frac{m_{\tilde{g}}}{m_{\tilde{q}}} = 2$ or even $\frac{m_{\tilde{g}}}{m_{\tilde{q}}} = 5$ depicted in fig. \ref{fig:TreeXsection5}. This reflects the gluino mass dependence explained in detail in section \ref{sec:PartProcesses}. See also \ref{fig:TreeXsection_fixed_m} for a visualization of this behavior.\\
Note also, that for sufficiently large squark masses squark production becomes the dominant process, see fig. \ref{fig:TreeXsection} and \ref{fig:TreeLevelSigma_0,9_2}. This is because the production of heavy particles requires large longitudinal momenta of the colliding partons, i.e. large $x$. Looking at the parton density functions in fig. \ref{fig:pdfs} one sees that within the proton the partons most likely to carry large momentum are quarks. So looking at large $x$ the proton basically consists of quarks and because the only process involving only quarks in the initial state is squark production, this channel dominates for high masses.\\
The total cross section in the MRSSM is increasingly smaller than in the MSSM in particular from about $\unit[500]{GeV}$ onwards. The is because for masses below that the $GG \to \tilde{q}\tilde{q}^\dagger$ channel, which is the same for both models, is the dominant one.\\
When raising the gluino squark mass ratio further to $\frac{m_{\tilde{g}}}{m_{\tilde{q}}} = 5$ the above described tendency continues. This is, all processes including a gluino get even more negligible and squark production gets further suppressed. While in the MSSM it becomes dominant over $GG \to \tilde{q}\tilde{q}^\dagger$ at $m_{\tilde{q}} \approx \unit[800]{GeV}$, it is subdominant in the MRSSM within the whole displayed mass range, even though it does not fall that steeply as the dominant channel.\\

\begin{figure}[!htpb]
\begin{center}
\includegraphics[scale=.4]{figures/mr=5_MSSM+MRSSM}
\includegraphics[scale=.45]{figures/rel_weights_mr=5_MSSM+MRSSM}
\caption{Hadronic cross section for squark and gluino production (in the first row) and relative contributions of the indicated final states to the total hadronic cross section (in the second row) in the MSSM (left-hand side) and MRSSM (right-hand side) at the LHC with $\sqrt{S} = \unit[13]{GeV}$. The ratio of gluino and squark mass is fixed to $5$. In the final state it has been summed over all squark flavors exept for staus. For the channels $qq \to \tilde{q}\tilde{q}$ and $qG \to \tilde{q}\tilde{G}$ also the charge conjugated process is included. The parton density functions and the renormalization and factorization scale are chosen as in fig. \ref{fig:TreeXsection}.}\label{fig:TreeXsection5}
\end{center}
\end{figure}
\newpage
The contour plots in fig. \ref{fig:ContourTree} underline the already mentioned difference between squark production in the MRSSM and the MSSM. While the cross sections for small gluino masses resemble each other closely, the cross section in the MRSSM gets increasingly suppressed with rising gluino mass. 
\begin{figure}[!htpb]
\begin{center}
\includegraphics[scale=.55]{figures/contour_MRSSM_squarks}
\includegraphics[scale=.55]{figures/contour_MSSM_squarks}
\caption{The squark (and antisquark) production cross section including five flavors in the MRSSM (top) and MSSM (bottom) at the LHC with $\sqrt{S} = \unit[13]{GeV}$. The parton density functions and the renormalization and factorization scale are chosen as in fig. \ref{fig:TreeXsection}.}\label{fig:ContourTree}
\end{center}
\end{figure}

>>>>

\sigma^B(q_i \overline{q}_j \to \tilde{q}\tilde{q}^\dagger) &= \delta_{ij}  \frac{g_s^4}{16\pi s} (n_f-1) \left[ \frac{4}{27} - \frac{16 m_{\tilde{q}}^2}{27s} \right]\beta_{\tilde{q}}\nonumber\\

@@

\subsubsection*{The Process $q_i \overline{q}_j \to \tilde{q}\tilde{q}^\dagger$}
The production of a squark and an antisquark through a quark and an antiquark in the initial state originates from two types of Feynman diagrams, see fig. \ref{fig:squarkantisquark}. The first one has an $s$-channel gluon and is the same in the MSSM and in the MRSSM. The second one exhibits a difference due to the $t$-channel gluino which is no Majorana particle in the MRSSM. 
\begin{figure}[!htbp]
\begin{center}
\begin{tikzpicture}[line width=1.0 pt, scale=1.3]
	\draw[fermion] (-1,0.5)--(-0.42,0);
	\draw[fermionbar] (-1,-0.5)--(-0.42,0);
	\draw[gluon] (-0.42,0)--(0.42,0); 
	\draw[scalar] (0.42,0)--(1,0.5);
	\draw[scalarbar] (0.42,0)--(1,-0.5);
\begin{scope}[shift={(3,0)}]
	\draw[fermion] (-1,0.5)--(0,0.5);
	\draw[fermionbar] (-1,-0.5)--(0,-0.5);
	\draw[fermionnoarrow] (0,0.5)--(0,-0.5);
	\draw[gluon] (0,0.5)--(0,-0.5); 
	\draw[scalar] (0,0.5)--(1,0.5);
	\draw[scalarbar] (0,-0.5)--(1,-0.5);
\end{scope}
\end{tikzpicture}
\caption{Tree level diagrams for $q\overline{q} \to \tilde{q}\tilde{q}^\dagger$}\label{fig:squarkantisquark}
\end{center}
\end{figure}
To see this one can either just apply the Feynman rules in Appendix \ref{sec:FeynmanRules} or think of the conservation of $R$-charge: Left handed squarks have R-charge $+1$ and right handed squarks have $R$-charge $-$1. Antiparticles have the opposite $R$-charge of their corresponding particles. The final state particles have to meet the total $R$-charge zero from the initial state. Because of this, one only has $\tilde{q}_L \tilde{q}^\dagger_L$ and $\tilde{q}_R \tilde{q}^\dagger_R$ as the final states in the MRSSM whereas in the MSSM one actually has four instead of two t-channel diagrams: The corresponding final states are $\tilde{q}_L \tilde{q}^\dagger_L$, $\tilde{q}_R \tilde{q}^\dagger_R$, $\tilde{q}_L \tilde{q}^\dagger_R$ and $\tilde{q}_R \tilde{q}^\dagger_L$. Consequently contributions from the $t$-channel diagrams are suppressed in the MRSSM in comparison to the MSSM. As shown in fig. \ref{fig:TreeXsection} this suppression grows with the masses. The reason for this lies in the gluino mass dependence of the $t$-channel diagrams which is explained in the discussion of squark production.\\
If the initial state quarks are of different flavor, the $s$-channel diagram is absent.

@@

\subsection{Results for Squark and Gluino Production at Tree-Level}\label{sec:tree-level_cross_sections}
%REFER TO Kribs, Martin: SNOWMASS WHITEPAPER\\
%REFER TO Vernoica Sanz: How many SUpersymmetries?\\
%\\
This section presents hadronic tree-level (Born) cross sections of squark and gluino production for two colliding protons in both, the MSSM and the MRSSM.\\
Note that in the following all possible production channels are taken into account. This is, for squark and squark-gluino production, also the charged conjugated processes, i.e. $\tilde{q}^\dagger\tilde{q}^\dagger$ and $\tilde{q}^\dagger\tilde{g}\left( \overline{\tilde{g}} \right)$, are included. In addition, squark production counts those processes twice which involve flavor unlike quarks, e.g. $ud \to \tilde{u}\tilde{d}$ is counted twice as the $d$-quark may come from either proton. This applies also to squark-antisquark production through a quark-antiquark pair.\\
The calculations have been performed by a $\texttt{C++}$ code which uses a library containing the absolute squared amplitudes for the processes in question. Note that the author has opted for the absolute squared amplitudes and not the partonic cross sections because this allows also for the calculation of partial differential cross sections, for possible future use. To perform the integration over the Mandelstam variable $t$ and $x_1$ and $x_2$, the routine ``Cuhre'' which is part of the \texttt{CUBA} library\cite{Hahn:2004fe} is used.\\
The following paragraph discusses fig. \ref{fig:TreeXsection}, \ref{fig:TreeLevelSigma_0,9_2} and \ref{fig:TreeXsection5}, i.e. the hadronic cross section of all considered processes for three successive mass ratios of gluino and squark: $\frac{m_{\tilde{g}}}{m_{\tilde{q}}} = 0.9,\ 2$ and $5$. Also, the corresponding fraction of final states is shown.
\begin{figure}[!htpb]
\begin{center}
\includegraphics[scale=.4]{figures/mr=0,9_MSSM+MRSSM}
\includegraphics[scale=.4]{figures/mr=2_MSSM+MRSSM}
\caption{Hadronic cross section for squark and gluino production in the MSSM (left-hand side) and MRSSM (right-hand side) at the LHC with $\sqrt{S} = \unit[13]{GeV}$. The ratio of gluino and squark mass is fixed to 0.9 (first row) and 2 (second row). In the final state it has been summed over all squark flavors exept for $t$-squarks. For the channels $qq \to \tilde{q}\tilde{q}$ and $qG \to \tilde{q}\tilde{G}$ also the charge conjugated process is included. The parton densities used are $\mathtt{MMHT2014LO}$ (LHAPDFID:$25000$) with $\alpha_s(M_Z) = 0.135$ in the 5-flavor scheme \cite{Harland-Lang:2014zoa}. As renormalization and factorization scale $\mu_R = \mu_F = \frac{m_1 + m_2}{2}$ has been chosen, where $m_i$ are the final state particle masses.} \label{fig:TreeXsection}
\end{center}
\end{figure}
\begin{figure}[!htpb]
\begin{center}
\includegraphics[scale=.4]{figures/rel_weights_mr=0,9_MSSM+MRSSM}
\includegraphics[scale=.4]{figures/rel_weights_mr=2_MSSM+MRSSM}
\caption{Relative contributions of the indicated final states on the total hadronic cross section in the MSSM (left-hand side) and MRSSM (right-hand side) at the LHC with \mbox{$\sqrt{S} = \unit[13]{GeV}$}. The ratio of gluino and squark mass is fixed to 0.9 (first row) and 2 (second row). In the final state it has been summed over all squark flavors exept for $t$-quarks. For the channels $qq \to \tilde{q}\tilde{q}$ and $qG \to \tilde{q}\tilde{G}$ also the charge conjugated process is included. The parton densities and the renormalization and factorization scale are chosen as in fig. \ref{fig:TreeXsection}.}\label{fig:TreeLevelSigma_0,9_2}
\end{center}
\end{figure}

For the small mass ratio $\frac{m_{\tilde{g}}}{m_{\tilde{q}}} = 0.9$ and small squark masses, the dominant contribution comes from gluino-squark production.
The subdominant channel is represented by gluino (antigluino) production which is much more pronounced in the MRSSM, which can be explained by the above mentioned factor of two difference in the $GG \to \tilde{g}\tilde{g}(\overline{\tilde{g}})$ channel which comes from the distinguishable gluino and antigluino in the MRSSM. Furthermore there is the above mentioned destructive interference term in the $q\overline{q} \to \tilde{g}\tilde{g}(\overline{\tilde{g}})$ channel which makes the cross section for this process in the MRSSM dominant over the one in the MSSM.\\
A salient difference between the MSSM and the MRSSM is that squark production is strongly suppressed in the MRSSM. While in the MSSM it becomes dominant above  $\approx \unit[2000]{GeV}$ it is at least subsubdominant for the whole displayed squark mass in the MRSSM. This suppression has already been explained above.\\
Turning from $\frac{m_{\tilde{g}}}{m_{\tilde{q}}} = 0.9$ to $\frac{m_{\tilde{g}}}{m_{\tilde{q}}} = 2$ suppresses quite strongly the production of gluinos in all pertaining channels. For the MSSM one finds above $\unit[500]{GeV}$ a growing dominance of squark production. The same happens in the MRSSM but for a significantly higher squark mass of about $\unit[1200]{GeV}$. This suppression of squark production in the MRSSM increases with a growing gluino masses which can be seen when going from $\frac{m_{\tilde{g}}}{m_{\tilde{q}}} = 0.9$ to  $\frac{m_{\tilde{g}}}{m_{\tilde{q}}} = 2$ or even $\frac{m_{\tilde{g}}}{m_{\tilde{q}}} = 5$ depicted in fig. \ref{fig:TreeXsection5}. This reflects the gluino mass dependence explained in detail in section \ref{sec:PartProcesses}. See also \ref{fig:TreeXsection_fixed_m} for a visualization of this behavior.\\
Note also, that for sufficiently large squark masses, squark production becomes the dominant process, see fig. \ref{fig:TreeXsection} and \ref{fig:TreeLevelSigma_0,9_2}. This is because the production of heavy particles requires large longitudinal momenta of the colliding partons, i.e. large $x$. Looking at the parton density functions in fig. \ref{fig:pdfs} one sees that within the proton the partons most likely to carry large momentum are quarks. So looking at large $x$ the proton basically consists of quarks and because the only process involving only quarks in the initial state is squark production, this channel dominates for high masses.\\
The total cross section in the MRSSM is increasingly smaller than in the MSSM, which can be seen for $\frac{m_{\tilde{g}}}{m_{\tilde{q}}} = 2$ when taking the  $GG \to \tilde{q}\tilde{q}^\dagger$ channel, which is the same for both models, as a benchmark.\\
When raising the gluino squark mass ratio further to $\frac{m_{\tilde{g}}}{m_{\tilde{q}}} = 5$ the above described tendency continues. This is, all processes including a gluino get even more negligible and squark production gets further suppressed. While in the MSSM it becomes dominant over $GG \to \tilde{q}\tilde{q}^\dagger$ at $m_{\tilde{q}} \approx \unit[700]{GeV}$, it is subdominant in the MRSSM within the whole displayed mass range, even though it does not fall that steeply as the dominant channel.\\

\begin{figure}[!htpb]
\begin{center}
\includegraphics[scale=.4]{figures/mr=5_MSSM+MRSSM}
\includegraphics[scale=.4]{figures/rel_weights_mr=5_MSSM+MRSSM}
\caption{Hadronic cross section for squark and gluino production (in the first row) and relative contributions of the indicated final states to the total hadronic cross section (in the second row) in the MSSM (left-hand side) and MRSSM (right-hand side) at the LHC with $\sqrt{S} = \unit[13]{GeV}$. The ratio of gluino and squark mass is fixed to $5$. In the final state it has been summed over all squark flavors exept for staus. For the channels $qq \to \tilde{q}\tilde{q}$ and $qG \to \tilde{q}\tilde{G}$ also the charge conjugated process is included. The parton density functions and the renormalization and factorization scale are chosen as in fig. \ref{fig:TreeXsection}.}\label{fig:TreeXsection5}
\end{center}
\end{figure}
\newpage
The contour plots in fig. \ref{fig:ContourTree} underline the already mentioned difference between squark production in the MRSSM and the MSSM. While the cross sections for small gluino masses resemble each other closely, the cross section in the MRSSM gets increasingly suppressed with rising gluino mass. 
\begin{figure}[!htpb]
\begin{center}
\includegraphics[scale=.55]{figures/contour_MRSSM_squarks}
\includegraphics[scale=.55]{figures/contour_MSSM_squarks}
\caption{The squark (and antisquark) production cross section including five flavors in the MRSSM (top) and MSSM (bottom) at the LHC with $\sqrt{S} = \unit[13]{GeV}$. The parton density functions and the renormalization and factorization scale are chosen as in fig. \ref{fig:TreeXsection}.}\label{fig:ContourTree}
\end{center}
\end{figure}

### 2017-10-17 Virt_Real.tex
updated TreeLevelPlots

\caption{A selection of diagrams contributing to the 1-loop matrix element for squark production. Each diagram is a representative of a certain topology. In the first line, an example for a self-energy and a vertex-correction diagram is shown. The second line lists typical box-diagrams: a three-point box and a four-point box.}\label{fig:1loopdiagrams}

@@

	\node [block2a] at (6,0) (Mreal) {$\mathcal{M}^{\mathrm{real}}$ is IR-divergent};

>>>>

\caption{A selection of diagrams contributing to the 1-loop matrix element for squark production. Each diagram is a representative of a certain topology. In the first line, an example for a self-energy and a vertex-correction diagram is shown. The second line lists typical box-diagrams: a three-point box and a four-point box.\newline
There are no loop corrections of external particles, which is expalined in section \ref{sec:LSZ}.}\label{fig:1loopdiagrams}

@@

	\node [block2a] at (6,0) (Mreal) {$\mathcal{M}^{\mathrm{R}}$ is IR-divergent};
